Quantum Interval-Valued Probability: Contextuality and the Born Rule

### 2017-08-14 prop_letter.tex
small wording

\paragraph*{QIVPMs and Classical IVPMs.} To formalize this connection,
we first note that contrary to the case with conventional quantum
probability spaces, there is generally no unique state consistent with
a QIVPM. We say that a QIVPM $\bar{\mu}$ is consistent with a state
$\rho$ and projector $P$ if the interval $\bar{\mu}(P)$ contains the
exact probability calculated by the Born rule, i.e, if:
\begin{equation}
\mu_{\rho}^{\mathrm{B}}\left(P\right)\in\bar{\mu}\left(P\right)
\end{equation}
where $\mu_{\rho}^{\mathrm{B}}\left(P\right)=\Tr\left(\rho P\right)$
is the probability that the event~$P$ happens determined by the Born
rule~\citep{Born1983,peres1995quantum,544199}.

We generalize this consistency relation to sets of states and general
subspaces of events as follows. A set of events $\events'$ is a
\emph{subspace} if it contains $\mathbb{0}$ and $\mathbb{1}$ and is
closed under complements and sums, i.e., for any
projector~$P\in\events'$, we have $\mathbb{1}-P\in\events'$ and for
each pair of orthogonal projectors~$P_0 \in \events'$ and
$P_1 \in \events'$, we have $(P_0 + P_1) \in \events'$. Given a
probability measure $\bar{\mu}$ and a subspace of events $\events'$,
we can collect the set of all states $\coreBorn(\bar{\mu},\events')$
that are consistent with $\bar{\mu}$ on every projector in $\events'$
as:
\begin{equation}
\coreBorn\left(\bar{\mu},\events'\right)=\set{\textrm{state }\rho}{\forall P\in \events',~\mu_{\rho}^{\mathrm{B}}\left(P\right)\in\bar{\mu}\left(P\right)}.
\end{equation}

>>>>

\paragraph*{QIVPMs and Classical IVPMs.} To formalize this connection,
we first note that contrary to the case with conventional quantum
probability spaces, there is generally no unique state $\rho$
consistent with a QIVPM. We say that a QIVPM $\bar{\mu}$ is consistent
with a state $\rho$ and projector $P$ if the interval $\bar{\mu}(P)$
contains the exact probability calculated by the Born rule, i.e, if:
\begin{equation}
\mu_{\rho}^{\mathrm{B}}\left(P\right)\in\bar{\mu}\left(P\right)
\end{equation}
where $\mu_{\rho}^{\mathrm{B}}\left(P\right)=\Tr\left(\rho P\right)$
is the probability that the event~$P$ happens determined by the Born
rule~\citep{Born1983,peres1995quantum,544199}.

We generalize this consistency relation to sets of states and general
subspaces of events as follows. A set of events $\events'$ is a
\emph{subspace} if it contains $\mathbb{0}$ and $\mathbb{1}$ and is
closed under complements and sums, i.e., for any
projector~$P\in\events'$, we have $\mathbb{1}-P\in\events'$ and for
each pair of orthogonal projectors~$P_0 \in \events'$ and
$P_1 \in \events'$, we have $(P_0 + P_1) \in \events'$. Given a
probability measure $\bar{\mu}$ and a subspace of events $\events'$,
we denote the collection $\coreBorn(\bar{\mu},\events')$ of all states
that are consistent with $\bar{\mu}$ on every projector in $\events'$
as:
\begin{equation}
\coreBorn\left(\bar{\mu},\events'\right)=\set{\rho}{\forall P\in \events',~\mu_{\rho}^{\mathrm{B}}\left(P\right)\in\bar{\mu}\left(P\right)}.
\end{equation}
